Market Expectations and Mangerial Turnover

### 2024-02-10 paper.qmd
updated repo

logit_baseline<-readRDS("./model/logit_poach_base.rds")
hazard_cty<-readRDS("./model/grp_lvl_poach_cty.rds")
hazard_season<-readRDS("./model/grp_lvl_poach_season.rds")
hazard_div <- readRDS("./model/grp_lvl_poach_div.rds")
logit_cty <-readRDS("./model/logit_grp_lvl_poach_cty.rds")
logit_div <- readRDS("./model/logit_grp_lvl_poach_div.rds")
logit_season <- readRDS("./model/logit_grp_lvl_poach_season.rds")

>>>>

logit_baseline<-readRDS("models/logit_poach_base.rds")
hazard_cty<-readRDS("models/grp_lvl_poach_cty.rds")
hazard_season<-readRDS("models/grp_lvl_poach_season.rds")
hazard_div <- readRDS("models/grp_lvl_poach_div.rds")
logit_cty <-readRDS("models/logit_grp_lvl_poach_cty.rds")
logit_div <- readRDS("models/logit_grp_lvl_poach_div.rds")
logit_season <- readRDS("models/logit_grp_lvl_poach_season.rds")
